25 years of Social Work Research

### 2015-03-29 dataCleaning.Rmd
Tableau edits.

---
title: "25 years of Social Work Research"
author: "Summary of Data Cleaning Procedures"
output: html_document
---

@@

```{r nsf, eval=FALSE}
nsf <- data.frame(c(238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280), as.factor(seq(2002,2012, 1)))
colnames(nsf) <- c("n.grads", "years")
```

@@

>>>>

---
title: "25 years of Social Work Research"
author: "Summary of Data Cleaning Procedures"
output: pdf_document
---

@@

```{r nsf, eval=FALSE}
nsf <- data.frame(c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280, NA), as.factor(seq(1989,2013, 1)))

growth <- c(rep("Unknown", 14), rep("Increase", 2), rep("Decrease", 3), "Increase", 
     rep("Decrease", 4), "Unknown")
nsf <- cbind(nsf, growth)

colnames(nsf) <- c("n.grads", "years", "growth")

write.csv(nsf, file="nsf.csv")

@@

```{r pages, eval=FALSE}
pages.df <- full.df %>% filter(attributes == "pages")
page.identifier <- grepl("[-p]", pages.df$record)
pages.df.reduced <- pages.df[page.identifier == FALSE,]

reduced <- full.df[full.df$articleID %in% pages.df.reduced$articleID, ]
reduced <- filter(reduced, attributes == "article" | attributes == "journal" | 
            attributes == "pubYear" | attributes == "pages" | attributes == "abstract")
